|

### 2021-09-22 article/articleCustomerDropoutMembership.Rmd
upd

plt.plot(clusters, meanDistortions, 'bx-')
plt.xlabel('k')
plt.ylabel('Average distortion')
plt.show()

@@

ax.legend()
ax.grid(True)
ax.set_title('Clusters clientes')
```

>>>>

plt.plot(clusters, meanDistortions, 'bx-')
plt.xlabel('k')
plt.ylabel('Average distortion')
plt.show();

@@

ax.legend()
ax.grid(True)
ax.set_title('Clusters clientes');
```
